Long-term Water Quality Change in Rhode Island Lakes and Ponds

### 2019-03-19 manuscript/manuscript.Rmd
Added paragraph to into and some citations

>>>>

Examining long term trends in Rhode Island lakes is possible because of the data gathered by University of Rhode Island’s Watershed Watch (URIWW).   URI’s Watershed Watch is a XX year-old citizen science project that has built a robust collaboration between URI scientists and a vast network of non-expert volunteer monitors.  Over the past XX years, volunteer monitors are trained and then collect *in situ* data as well as whole water samples during the growing season.  These types of citizen science efforts allow for the collection of reliable data that in turn lead to crucial and frequently unexpected insights [@dickinson2012current; @kosmala2016assessing].  Often due to lack of resources, these efforts would not happen otherwise.  Here specifically, URIWW data contributed to not only the larger subcontinent extent study, but also allowed us to examine the long-term trends of Rhode Island.
